### 2021-04-28 LaTeX-ACM/sections/paper.tex
edits on the paper

For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology. New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight. Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets. Such exchanges are a key component to blockchain-based economic activity.

Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets. They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet. Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers. More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain. In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.

@@

\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}. We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark). Generally if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.

Our proof-of-concept, \cm, is an extensible base class suitable for experiments. \cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third party; all operations are transparent; and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders. In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).

While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings, \etc). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}. While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.

@@

A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge. In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp. Every execution of every function call is a validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power). Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order. For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.

@@

\subsection{Trading Blockchain-based Assets}

@@

\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

@@

In this paper, we focus on benchmarking an order book for the public blockchain Ethereum. Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment. Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol. Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.

\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees. By contrast, an order book requires no upfront inventory and trading fees are optional. Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.

\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality. Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook). A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders. An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}).

@@

\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}. Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order. If the prices overlap, the miner keeps the difference (which they could extract anyways through front-running). Call markets largely side-step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}). The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014). Market operations are part of the blockchain logic.

@@

\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution. Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}. A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges. Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an order book, however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is. We later compare it to our variant with roll-ups in Section~\ref{sec:rollups}. The main overlap is our common focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

@@

In designing \cm within Ethereum's gas model, performance is the main bottleneck. For a call market, closing the market and processing all the orders is the most time consuming step. The most critical design decision is the data structure for holding orders. While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.

When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks. In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled. The only exceptions are in the case of a tie on price or a cancelled order, both of which we return to later. For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price. Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.

@@

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implement a PQ with a heap that stores its data in a dynamically-sized array.

\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated. To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.

@@

\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache. We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance. A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}. We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant. The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.

@@

\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty. The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}. These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage. Recall this results in a gas refund. Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction). In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worse based on how much of a refund they generate.

\paragraph{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest. This is in accordance with the theoretical worst-case time complexity for each. However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor. For these reasons, we suggest using a linked list variant for this specific application. As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new DApp. Accordingly, we choose to implement the call market with the linked list with mapping. Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).

@@

\subsection{Cost/Benefit of Cleaning up After Yourself}
\label{sec:gasrefund}

@@

\paragraph{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to). For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means). Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte-string for non-integers) in the current state (uninitialized variables in Ethereum have the value zero by default). Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.

For this reason, some EVM operations cost a negative amount of gas. That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with a 11M limit). Negative gas operations include:

@@

\item \texttt{SELFDESTRUCT}. This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address. \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain. It always refunds 24,000 gas. For example, if a contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).

@@

At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}. So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually. First we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.

@@

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today. As our previous experiments indicated, the choice of PQ implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

@@

The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.

@@

\subsection{Cleaning Up Revisted}

@@

In Solidity, it is not possible to delete an entire mapping without individually zero-ing out each entry key-by-key. At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again. The following are some options for addressing this conflict.

@@

We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX). We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

%A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}). In the case of (1), validating the proof must be cheaper than running the function itself. There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

>>>>

For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology. New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight. Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets. Such exchanges are key components to blockchain-based economic activity.

Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets. They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet. Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favor of running on centralized servers. More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain. In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.

@@

\textbf{Contributions.} We study fully on-chain markets through design and implementation with Solidity---a high-level programming language for Ethereum that is syntactically similar to Java~\cite{Ethereum41:online}. We choose Ethereum as a hostile environment for an order book: Ethereum is fully decentralized (hardest to regulate), network participation is open to anyone on the internet (strongest adversarial model), and, as a result, it is slow (a lower-bound benchmark). Generally, if an application is feasible on Ethereum, it will also be feasible and only run faster on a private (or permissioned) blockchain (\eg Hyperledger), which is a blockchain operated by authorized network nodes only, generally visible to regulators.

Our proof-of-concept, \cm, is an extensible base class suitable for experiments. \cm is designed from a security perspective: users only trust their assets to \cm's auditable code (non-custodial) and not to a third part, all operations are transparent, and we nearly eliminate the ability for adversarial network nodes to profit from front-running orders. In fact, we believe we are the first to design a decentralized application that actually leverages front-running (\ie miner extractable value~\cite{daian2019flash}) for the benefit of the system (see Section~\ref{sec:close}).

While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}. While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.

@@

A public blockchain is an open peer-to-peer network that maintains a set of transactions without a single entity in charge. In Ethereum, \emph{transactions} encode the bytecode of user-written \emph{decentralized applications} (DApps) to be stored on the blockchain; and the function calls made to the DApp. Every execution of every function call is validated by all honest, participating nodes to correct; a property that is robust against a fraction of faulty and malicious network nodes (or more precisely, their accumulated computational power). Once transactions are agreed upon, all honest participants will have identical sets of transactions in the same order. For Ethereum, this is conceptualized as the current state of a large \emph{virtual machine (EVM)} that is running many DApps.

@@

\subsection{Trading Blockchain-Based Assets}

@@

\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been leveled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

@@

In this paper, we focus on benchmarking an order book for the public blockchain Ethereum. Ethereum is widely used and we stand to learn the most from working in a performance-hostile environment. Exchanges could be given their own dedicated blockchain, where trade execution logic can be coded into the network protocol. Trading systems on permissioned blockchains (\eg NASDAQ Linq, tZero) can also improve execution time and throughput, but they reduce user transparency and trust if unregulated.

\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fueled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees. By contrast, an order book requires no upfront inventory and trading fees are optional. Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.

\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality. Such decentralized exchanges (DEXes) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook). A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair, funds can still be indirectly stolen by a malicious exchange executing unauthorized trades, and server downtime is a common frustration for traders. An enhancement is to prove that trade execution is correct (\eg Loopring) but these proofs have blind spots (discussed in section~\ref{sec:rollups}).

@@

\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}. Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order. If the prices overlap, the miner keeps the difference (which they could extract regardless through front-running). Call markets largely side step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}). The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014). Market operations are part of the blockchain logic.

@@

\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books, but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution. Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}. A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges. Atomic swaps (\ie payment vs. delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an order book; however, it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is. We later compare it to our variant with roll-ups in Section~\ref{sec:rollups}. The main overlap is our common focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third-party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

@@

In designing \cm within Ethereum's gas model, performance is the main bottleneck. For a call market, closing the market and processing all the orders are the most time-consuming steps. The most critical design decision is the data structure for holding orders. While data structures are well studied for many languages, Solidity/EVM has its own unique aspects (\eg gas refunds, a relatively cheap mapping data structure, only partial support for object-oriented programming) that create difficulties in assessing which will perform best without actually deploying and evaluating each variant.

When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks. In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled. The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later. For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price. Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.

@@

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of the tree are in a specific order, and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implement a PQ with a heap that stores its data in a dynamically sized array.

\item \textbf{Heap with Static Array.} A heap can also be represented by a Solidity storage array in which the storage is statically allocated. To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.

@@

\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache. We tried a variety of tests (including testing the full-call market with each variant) with consistent results in performance. A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}. We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant. The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.

@@

\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty. The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}. These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage. Recall this results in a gas refund. Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction). In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund. However, none of them are better or worse based on how much of a refund they generate.

\paragraph{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest. This is in accordance with the theoretical worst-case time complexity for each. However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behavior is not a significant factor. For these reasons, we suggest using a linked list variant for this specific application. As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new DApp. Accordingly, we choose to implement the call market with the linked list with mapping. Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).

@@

\subsection{Cost/Benefit of Cleaning Up After Yourself}
\label{sec:gasrefund}

@@

\paragraph{Gas Refunds.} In order to reconstruct the current state of Ethereum's EVM, a node must obtain a copy of every variable change since the genesis block (or a more recent `checkpoint' that is universally agreed to). For this reason, stored variables persist for a long time and, at first glance, it seems pointless to free up variable storage (and unclear what `free up' even means). Once the current state of the EVM is established by a node, it can forget about every historical variable changes and only concern itself with the variables that have non-zero value (as a byte string for non-integers) in the current state (uninitialized variables in Ethereum have the value 0 by default). Therefore, freeing up variables will reduce the amount of state Ethereum nodes need to maintain going forward.

For this reason, some EVM operations cost a negative amount of gas. That is, the gas is refunded to the sender at the end of the transaction, however (1) the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit). Negative gas operations include:

@@

\item \texttt{SELF-DESTRUCT}. This operation destroys the contract that calls it and refunds its balance (if any) to a designated receiver address. The  \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain. It always refunds 24,000 gas. For example, if contract A stores a single non-zero integer and contract B stores 100 non-zero integers, the \texttt{SELFDESTRUCT} refund for both is the same (24,000 gas).

@@

At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}. So in order to account for refunds in Tables~\ref{tab:PQUnitTests}, we calculate them manually. First, we need to figure out exactly how much storage is being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 and 15,000 respectively.

@@

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today. As our previous experiments indicated, the choice of PQ implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we were also interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

@@

The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.

@@

\subsection{Cleaning Up Revisited}

@@

In Solidity, it is not possible to delete an entire mapping without individually zeroing out each entry key-by-key. At the same time, it is wasteful to let an entire mapping sit in the EVM when it will never be referenced again. The following are some options for addressing this conflict.

@@
